\pkg{cubble}: An \proglang{R} Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2023-07-04 cubble.Rmd
section 4.3

The matching or pairing results can also be returned as a list of matched cubbles, by setting the argument \code{return_cubble = TRUE}. After excluding the two pairs where a river station is matched to more than one weather stations (river station 226027 is matched twice in group 3 and 5 and similarly for station 230200 in group 7 and 8), all the results can be combined into a single cubble using \code{bind_rows()},

@@

To match the water level and precipitation time series across the matched locations, the function \code{match_temporal()} is used with the variables \code{group} and \code{types} identifying the matching group and the two data sources:

@@

Similarly, the cubble output can be returned using the argument \code{return_cubble = TRUE}. Here, we select the four pairs of time series (precipitation/water level) with the highest number of matching peaks and show them on the map (a). The time series of river levels is standardize for better comparison  in Figure \ref{fig:matching} panel (b).

>>>>

The results can also be returned as a list of matched cubbles, by setting the argument \code{return_cubble = TRUE}. After excluding the two pairs where a river station is matched to more than one weather stations (river station 226027 is matched twice in group 3 and 5 and similarly for station 230200 in group 7 and 8), all the results can be combined into a single cubble using \code{bind_rows()},

@@

To match the water level and precipitation time series across the matched locations, the function \code{match_temporal()} is used with the variables \code{group} and \code{type} identifying the matching group and the two data sources:

@@

Similarly, the cubble output can be returned using the argument \code{return_cubble = TRUE}. Here, we select the four pairs of time series (precipitation/water level) with the highest number of matching peaks and show them on the map (Figure \ref{fig:matching} a). The time series of river levels is standardized to make the comparison easier in panel (b).
